---
title: "KPI Forecast"
author: "Luke Buaas"
date: "2025-03-28"
output: html_document
---

---
title: "All_Forecasts"
author: "Luke Buaas"
date: "2024-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load Libraries
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(lubridate)) install.packages("lubridate", repos = "http://cran.us.r-project.org")
if(!require(gridExtra)) install.packages("gridExtra", repos = "http://cran.us.r-project.org")
if(!require(timetk)) install.packages("timetk", repos = "http://cran.us.r-project.org")
if(!require(reshape2)) install.packages("reshape2", repos = "https://cran.us.r-project.org")
if(!require(Boruta)) install.packages("Boruta", repos = "https://cran.us.r-project.org")
if(!require(imputeTS)) install.packages("imputeTS", repos = "https://cran.us.r-project.org")
if(!require(modeltime)) install.packages("modeltime", repos = "https://cran.us.r-project.org")
if(!require(parsnip)) install.packages("parsnip", repos = "https://cran.us.r-project.org")
if(!require(recipes)) install.packages("recipes", repos = "https://cran.us.r-project.org")
if(!require(workflows)) install.packages("workflows", repos = "https://cran.us.r-project.org")
if(!require(readxl)) install.packages("readxl", repos = "https://cran.us.r-project.org")
if(!require(rsample)) install.packages("rsample", repos = "https://cran.us.r-project.org")
if(!require(glmnet)) install.packages("glmnet", repos = "https://cran.us.r-project.org")
```


######################################################################################
#
# KPI_1
#
######################################################################################

####
# Cust_type_1
###

```{r}
# Load in Raw Data
df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)

###################################################################

df_KPI_1 <- left_join(df_KPI_1, df_promos, by = "Date")

head(df_KPI_1)
```

```{r}
df_KPI_1 %>%
  ggplot(aes(Date, KPI_1)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

Detrends Data to check for seasonality
```{r}
# STL Decomposition
detrended_KPI_1 <- df_KPI_1
stl_decomposition <- stl(ts(detrended_KPI_1$KPI_1, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_KPI_1$detrended_stl <- detrended_KPI_1$KPI_1 - trend_component

# Visualize
ggplot(detrended_KPI_1, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_KPI_1$detrended_stl, lag.max = nrow(detrended_KPI_1), xlab="Lag (years)")
pacf(detrended_KPI_1$detrended_stl, lag.max = nrow(detrended_KPI_1), xlab="Lag (years)")

rm(detrended_KPI_1,stl_decomposition,trend_component)
```


```{r}
df_KPI_1 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_1 <- df_KPI_1 %>%
  arrange(Date) %>%
  mutate(KPI_1_lag1 = lag(KPI_1, 1),
         KPI_1_lag3 = lag(KPI_1, 3),
         KPI_1_lag6 = lag(KPI_1, 6),          
         KPI_1_lag9 = lag(KPI_1, 9),
         KPI_1_lag12 = lag(KPI_1, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_KPI_1, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_1,.interactive = TRUE)
```

Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets_2 <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets_3 <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_ets_2,
    fit_ets_3,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_ets_2,
    fit_ets_3,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_1
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```

```{r}
dates <- KPI_1(df_KPI_1$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_1 %>% select(Date,KPI_1), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(KPI_1_lag1 = lag(KPI_1, 1),
         KPI_1_lag3 = lag(KPI_1, 3),
         KPI_1_lag6 = lag(KPI_1, 6),          
         KPI_1_lag9 = lag(KPI_1, 9),
         KPI_1_lag12 = lag(KPI_1, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_KPI_1_data <- df_combined %>%
  filter(!(is.na(KPI_1)))

new_data <- df_combined %>%
  filter(is.na(KPI_1)) %>%
  select(-KPI_1) %>%
  filter(!(is.na(KPI_1_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_KPI_1_data
  
  modeltime_actual_data_format <- actual_KPI_1_data %>% 
      mutate(
        .index = Date,
        .value = KPI_1,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           KPI_1_lag1,KPI_1_lag3,KPI_1_lag6,KPI_1_lag9,KPI_1_lag12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_1)) %>% # Remove NAs in KPI_1
                        filter(!is.na(KPI_1_lag1)) %>% # Remove NAs in KPI_1_lag1
                        filter(!is.na(KPI_1_lag3)) %>%
                        filter(!is.na(KPI_1_lag6)) %>%
                        filter(!is.na(KPI_1_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_1 = forecasted_value,
                           KPI_1_lag1 = NA,
                           KPI_1_lag3 = NA,
                           KPI_1_lag6 = NA,
                           KPI_1_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_1 = if_else(Date == next_date, forecasted_value, KPI_1),
        KPI_1_lag1 = lag(KPI_1, 1),
        KPI_1_lag3 = lag(KPI_1, 3),
        KPI_1_lag6 = lag(KPI_1, 6),          
        KPI_1_lag9 = lag(KPI_1, 9),
        KPI_1_lag12 = lag(KPI_1, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_1)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_1)) %>%
      select(-KPI_1) %>%
      filter(!(is.na(KPI_1_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/Cust_type_1_KPI_1Purchasers_forecast.csv")
```

###
# Cust_type_2
###


```{r}
# Load in Raw Data
df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)

###################################################################

df_KPI_1 <- left_join(df_KPI_1, df_promos, by = "Date")

head(df_KPI_1)
```

```{r}
df_KPI_1 %>%
  ggplot(aes(Date, KPI_1)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

Detrends data
```{r}
# STL Decomposition
detrended_KPI_1 <- df_KPI_1
stl_decomposition <- stl(ts(detrended_KPI_1$KPI_1, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_KPI_1$detrended_stl <- detrended_KPI_1$KPI_1 - trend_component

# Visualize
ggplot(detrended_KPI_1, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_KPI_1$detrended_stl, lag.max = nrow(detrended_KPI_1), xlab="Lag (years)")
pacf(detrended_KPI_1$detrended_stl, lag.max = nrow(detrended_KPI_1), xlab="Lag (years)")

rm(detrended_KPI_1,stl_decomposition,trend_component)
```

```{r}
df_KPI_1 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_1 <- df_KPI_1 %>%
  arrange(Date) %>%
  mutate(KPI_1_lag1 = lag(KPI_1, 1),
         KPI_1_lag3 = lag(KPI_1, 3),
         KPI_1_lag6 = lag(KPI_1, 6),          
         KPI_1_lag9 = lag(KPI_1, 9),
         KPI_1_lag12 = lag(KPI_1, 12)) %>%  
  drop_na()

Splits <- initial_time_split(lag_df_KPI_1, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_1,.interactive = TRUE)
```


Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets_2 <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets_3 <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_ets_2,
    fit_ets_3,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_ets_2,
    fit_ets_3,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_1
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```

```{r}
dates <- KPI_1(df_KPI_1$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_1 %>% select(Date,KPI_1), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(KPI_1_lag1 = lag(KPI_1, 1),
         KPI_1_lag3 = lag(KPI_1, 3),
         KPI_1_lag6 = lag(KPI_1, 6),          
         KPI_1_lag9 = lag(KPI_1, 9),
         KPI_1_lag12 = lag(KPI_1, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_KPI_1_data <- df_combined %>%
  filter(!(is.na(KPI_1)))

new_data <- df_combined %>%
  filter(is.na(KPI_1)) %>%
  select(-KPI_1) %>%
  filter(!(is.na(KPI_1_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_KPI_1_data
  
  modeltime_actual_data_format <- actual_KPI_1_data %>% 
      mutate(
        .index = Date,
        .value = KPI_1,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           KPI_1_lag1,KPI_1_lag3,KPI_1_lag6,KPI_1_lag9,KPI_1_lag12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_1)) %>% # Remove NAs in KPI_1
                        filter(!is.na(KPI_1_lag1)) %>% # Remove NAs in KPI_1_lag1
                        filter(!is.na(KPI_1_lag3)) %>%
                        filter(!is.na(KPI_1_lag6)) %>%
                        filter(!is.na(KPI_1_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_1 = forecasted_value,
                           KPI_1_lag1 = NA,
                           KPI_1_lag3 = NA,
                           KPI_1_lag6 = NA,
                           KPI_1_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_1 = if_else(Date == next_date, forecasted_value, KPI_1),
        KPI_1_lag1 = lag(KPI_1, 1),
        KPI_1_lag3 = lag(KPI_1, 3),
        KPI_1_lag6 = lag(KPI_1, 6),          
        KPI_1_lag9 = lag(KPI_1, 9),
        KPI_1_lag12 = lag(KPI_1, 12))
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_1)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_1)) %>%
      select(-KPI_1) %>%
      filter(!(is.na(KPI_1_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/Cust_type_2_KPI_1Purchasers_forecast.csv")
```


###
# Actual
###


```{r}
# Load in Raw Data
df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, KPI_1_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_3 = as.integer(Promo_3),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12))  %>%
  select(-Promo_12) %>%
  select(-Promo_12)

###################################################################
# READS Cust_type_1 DATA.
###################################################################
df_Cust_type_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_Purchasers)

names(df_Cust_type_1) <- c("Date", "Cust_type_1")

df_Cust_type_1_Forecast <- read_csv("forecasts/Cust_type_1_KPI_1Purchasers_forecast.csv")

# df_KPI_1_Forecast$.index <- mdy(df_KPI_1_Forecast$.index)

df_Cust_type_1_Forecast <- df_Cust_type_1_Forecast[,c(1,4)]

names(df_Cust_type_1_Forecast) <- c("Date", "Cust_type_1")

df_Cust_type_1 <- rbind(df_Cust_type_1, df_Cust_type_1_Forecast)

rm(df_Cust_type_1_Forecast)


###################################################################
# READS Cust_type_2 DATA. NOT NEEDED
###################################################################
df_Cust_type_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Purchasers)

names(df_Cust_type_2) <- c("Date", "Cust_type_2")

df_Cust_type_2_Forecast <- read_csv("forecasts/Cust_type_2_KPI_1Purchasers_forecast.csv")

# df_KPI_1_Forecast$.index <- mdy(df_KPI_1_Forecast$.index)

df_Cust_type_2_Forecast <- df_Cust_type_2_Forecast[,c(1,4)]

names(df_Cust_type_2_Forecast) <- c("Date", "Cust_type_2")

df_Cust_type_2 <- rbind(df_Cust_type_2, df_Cust_type_2_Forecast)

rm(df_Cust_type_2_Forecast)
###################################################################

df_promos <- left_join(df_promos, df_Cust_type_1, by = "Date")
df_promos <- left_join(df_promos, df_Cust_type_2, by = "Date")
df_KPI_1 <- left_join(df_KPI_1, df_promos, by = "Date")

head(df_KPI_1)
```

```{r}
df_KPI_1 %>%
  ggplot(aes(Date, KPI_1)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

detrends data
```{r}
# STL Decomposition
detrended_KPI_1 <- df_KPI_1
stl_decomposition <- stl(ts(detrended_KPI_1$KPI_1, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_KPI_1$detrended_stl <- detrended_KPI_1$KPI_1 - trend_component

# Visualize
ggplot(detrended_KPI_1, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_KPI_1$detrended_stl, lag.max = nrow(detrended_KPI_1), xlab="Lag (years)")
pacf(detrended_KPI_1$detrended_stl, lag.max = nrow(detrended_KPI_1), xlab="Lag (years)")

rm(detrended_KPI_1,stl_decomposition,trend_component)
```


```{r}
df_KPI_1 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_1 <- df_KPI_1 %>%
  arrange(Date) %>%
  mutate(KPI_1_lag1 = lag(KPI_1, 1),
         KPI_1_lag3 = lag(KPI_1, 3),
         KPI_1_lag6 = lag(KPI_1, 6),          
         KPI_1_lag9 = lag(KPI_1, 9),
         KPI_1_lag12 = lag(KPI_1, 12)) %>%
  filter(!(Date < "2020-01-01"))

Splits <- initial_time_split(lag_df_KPI_1, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_1,.interactive = TRUE)
```

Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_1 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels

# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_1
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_KPI_1$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11,Cust_type_1, Cust_type_2)#, Promo_12) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_1 %>% select(Date,KPI_1), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(KPI_1_lag1 = lag(KPI_1, 1),
         KPI_1_lag3 = lag(KPI_1, 3),
         KPI_1_lag6 = lag(KPI_1, 6),          
         KPI_1_lag9 = lag(KPI_1, 9),
         KPI_1_lag12 = lag(KPI_1, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_KPI_1_data <- df_combined %>%
  filter(!(is.na(KPI_1)))

new_data <- df_combined %>%
  filter(is.na(KPI_1)) %>%
  select(-KPI_1) %>%
  filter(!(is.na(KPI_1_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_KPI_1_data
  
  modeltime_actual_data_format <- actual_KPI_1_data %>% 
      mutate(
        .index = Date,
        .value = KPI_1,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           KPI_1_lag1,KPI_1_lag3,KPI_1_lag6,KPI_1_lag9,KPI_1_lag12,Cust_type_1,Cust_type_2)#,Promo_12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_1)) %>% # Remove NAs in KPI_1
                        filter(!is.na(KPI_1_lag1)) %>% # Remove NAs in KPI_1_lag1
                        filter(!is.na(KPI_1_lag3)) %>%
                        filter(!is.na(KPI_1_lag6)) %>%
                        filter(!is.na(KPI_1_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_1 = forecasted_value,
                           KPI_1_lag1 = NA,
                           KPI_1_lag3 = NA,
                           KPI_1_lag6 = NA,
                           KPI_1_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_1 = if_else(Date == next_date, forecasted_value, KPI_1),
        KPI_1_lag1 = lag(KPI_1, 1),
        KPI_1_lag3 = lag(KPI_1, 3),
        KPI_1_lag6 = lag(KPI_1, 6),          
        KPI_1_lag9 = lag(KPI_1, 9),
        KPI_1_lag12 = lag(KPI_1, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_1)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_1)) %>%
      select(-KPI_1) %>%
      filter(!(is.na(KPI_1_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/KPI_1Purchasers_forecast.csv")
```


######################################################################################
#
# SALES
#
######################################################################################


###
# Cust_type_1
###


```{r}
# Load in Raw Dat
df_sales <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_Sales)

names(df_sales) <- c("Date", "Sales")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),         
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12)

#########################################

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/Cust_type_1_KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)

###################################################################

df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
df_sales <- left_join(df_sales, df_promos, by = "Date")

head(df_sales)
```

```{r}
df_sales %>%
  ggplot(aes(Date, Sales)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "Native Sales - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

detrends data
```{r}
# STL Decomposition
detrended_sales <- df_sales
stl_decomposition <- stl(ts(detrended_sales$Sales, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_sales$detrended_stl <- detrended_sales$Sales - trend_component

# Visualize
ggplot(detrended_sales, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Create a time series object for detrended_stl with the correct frequency and start period
detrended_stl_ts <- ts(detrended_sales$detrended_stl, frequency = 12, start = c(year(min(detrended_sales$Date)), month(min(detrended_sales$Date))))

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_stl_ts, lag.max = nrow(detrended_sales), xlab="Lag (years)")
pacf(detrended_stl_ts, lag.max = nrow(detrended_sales), xlab="Lag (years)")

rm(detrended_sales,detrended_stl_ts,stl_decomposition,trend_component)
```

```{r}
df_sales %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_sales <- df_sales %>%
  arrange(Date) %>%
  mutate(Sales_lag1 = lag(Sales, 1),
         Sales_lag3 = lag(Sales, 3),
         Sales_lag6 = lag(Sales, 6),
         Sales_lag9 = lag(Sales, 9),
         Sales_lag12 = lag(Sales, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_sales, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, Sales,.interactive = TRUE)
```


Model Pre-Processing
```{r}
recipe_spec <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels

# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels

# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_sales
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_sales$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11, KPI_1, Promo_12) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(KPI_1 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_sales %>% select(Date,Sales), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(Sales_lag1 = lag(Sales, 1),
         Sales_lag3 = lag(Sales, 3),
         Sales_lag6 = lag(Sales, 6),
         Sales_lag9 = lag(Sales, 9),
         Sales_lag12 = lag(Sales, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(Sales)))

new_data <- df_combined %>%
  filter(is.na(Sales)) %>%
  select(-Sales) %>%
  filter(!(is.na(Sales_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = Sales,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,Sales,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           Promo_12,Sales_lag1,Sales_lag3,Sales_lag6,Sales_lag9,Sales_lag12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(Sales)) %>% # Remove NAs in Sales
                        filter(!is.na(Sales_lag1)) %>%  # Remove NAs in Sales_lag1
                        filter(!is.na(Sales_lag3)) %>%
                        filter(!is.na(Sales_lag6)) %>%
                        filter(!is.na(Sales_lag9)) %>%
                        filter(!is.na(Sales_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           Sales = forecasted_value,
                           Sales_lag1 = NA,
                           Sales_lag3 = NA,
                           Sales_lag6 = NA,
                           Sales_lag9 = NA,
                           Sales_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        Sales = if_else(Date == next_date, forecasted_value, Sales),
        Sales_lag1 = lag(Sales, 1),
        Sales_lag3 = lag(Sales, 3),
        Sales_lag6 = lag(Sales, 6),
        Sales_lag9 = lag(Sales, 9),
        Sales_lag12 = lag(Sales, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(Sales)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(Sales)) %>%
      select(-Sales) %>%
      filter(!(is.na(Sales_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/Cust_type_1_NativeSales_forecast.csv")
```


###
# Cust_type_2
###


```{r}
# Load in Raw Dat
df_sales <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Sales)

names(df_sales) <- c("Date", "Sales")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12)

#########################################

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/Cust_type_2_KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)

###################################################################

df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
df_sales <- left_join(df_sales, df_promos, by = "Date")

head(df_sales)
```

```{r}
df_sales %>%
  ggplot(aes(Date, Sales)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "Native Sales - Japan",
       x = "",
       y = "") + 
  theme_classic()
```
detrends sales
```{r}
# STL Decomposition
detrended_sales <- df_sales
stl_decomposition <- stl(ts(detrended_sales$Sales, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_sales$detrended_stl <- detrended_sales$Sales - trend_component

# Visualize
ggplot(detrended_sales, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_sales$detrended_stl, lag.max = 20)
pacf(detrended_sales$detrended_stl, lag.max = 20)

rm(detrended_sales)
```

```{r}
df_sales %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_sales <- df_sales %>%
  arrange(Date) %>%
  mutate(Sales_lag1 = lag(Sales, 1),
         Sales_lag3 = lag(Sales, 3),
         Sales_lag6 = lag(Sales, 6),
         Sales_lag9 = lag(Sales, 9),
         Sales_lag12 = lag(Sales, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_sales, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, Sales,.interactive = TRUE)
```



Model Pre-Processing
```{r}
recipe_spec <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_sales
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_sales$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11, KPI_1, Promo_12) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(KPI_1 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_sales %>% select(Date,Sales), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(Sales_lag1 = lag(Sales, 1),
         Sales_lag3 = lag(Sales, 3),
         Sales_lag6 = lag(Sales, 6),
         Sales_lag9 = lag(Sales, 9),
         Sales_lag12 = lag(Sales, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(Sales)))

new_data <- df_combined %>%
  filter(is.na(Sales)) %>%
  select(-Sales) %>%
  filter(!(is.na(Sales_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = Sales,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,Sales,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           Promo_12,Sales_lag1,Sales_lag3,Sales_lag6,Sales_lag9,Sales_lag12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(Sales)) %>% # Remove NAs in Sales
                        filter(!is.na(Sales_lag1)) %>%  # Remove NAs in Sales_lag1
                        filter(!is.na(Sales_lag3)) %>%
                        filter(!is.na(Sales_lag6)) %>%
                        filter(!is.na(Sales_lag9)) %>%
                        filter(!is.na(Sales_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           Sales = forecasted_value,
                           Sales_lag1 = NA,
                           Sales_lag3 = NA,
                           Sales_lag6 = NA,
                           Sales_lag9 = NA,
                           Sales_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        Sales = if_else(Date == next_date, forecasted_value, Sales),
        Sales_lag1 = lag(Sales, 1),
        Sales_lag3 = lag(Sales, 3),
        Sales_lag6 = lag(Sales, 6),
        Sales_lag9 = lag(Sales, 9),
        Sales_lag12 = lag(Sales, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(Sales)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(Sales)) %>%
      select(-Sales) %>%
      filter(!(is.na(Sales_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/Cust_type_2_NativeSales_forecast.csv")
```


###
# Actual
###


```{r}
# Load in Raw Data
df_sales <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Native_Sales)

names(df_sales) <- c("Date", "Sales")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12)

#########################################

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, KPI_1_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)

###################################################################

# Adds Cust_type_1 & Cust_type_2 data NOT NEEDED

df_Cust_type_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_Sales)

names(df_Cust_type_1) <- c("Date", "Cust_type_1")

df_Cust_type_1_Forecast <- read_csv("forecasts/Cust_type_1_NativeSales_forecast.csv")

# df_KPI_1_Forecast$.index <- mdy(df_KPI_1_Forecast$.index)

df_Cust_type_1_Forecast <- df_Cust_type_1_Forecast[,c(1,4)]

names(df_Cust_type_1_Forecast) <- c("Date", "Cust_type_1")

df_Cust_type_1 <- rbind(df_Cust_type_1, df_Cust_type_1_Forecast)

rm(df_Cust_type_1_Forecast)
###################################################################

df_Cust_type_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Sales)

names(df_Cust_type_2) <- c("Date", "Cust_type_2")

df_Cust_type_2_Forecast <- read_csv("forecasts/Cust_type_2_NativeSales_forecast.csv")

# df_KPI_1_Forecast$.index <- mdy(df_KPI_1_Forecast$.index)

df_Cust_type_2_Forecast <- df_Cust_type_2_Forecast[,c(1,4)]

names(df_Cust_type_2_Forecast) <- c("Date", "Cust_type_2")

df_Cust_type_2 <- rbind(df_Cust_type_2, df_Cust_type_2_Forecast)

#rm(df_Cust_type_2_Forecast)
###################################################################

df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
df_promos <- left_join(df_promos, df_Cust_type_1, by = "Date")
df_promos <- left_join(df_promos, df_Cust_type_2, by = "Date")
df_sales <- left_join(df_sales, df_promos, by = "Date")


head(df_sales)
```

```{r}
df_sales %>%
  ggplot(aes(Date, Sales)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "Native Sales - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

detrends sales
```{r}
# STL Decomposition
detrended_sales <- df_sales
stl_decomposition <- stl(ts(detrended_sales$Sales, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_sales$detrended_stl <- detrended_sales$Sales - trend_component

# Visualize
ggplot(detrended_sales, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Create a time series object for detrended_stl with the correct frequency and start period
detrended_stl_ts <- ts(detrended_sales$detrended_stl, frequency = 12, start = c(year(min(detrended_sales$Date)), month(min(detrended_sales$Date))))

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_stl_ts, lag.max = nrow(detrended_sales), xlab="Lag (years)")
pacf(detrended_stl_ts, lag.max = nrow(detrended_sales), xlab="Lag (years)")

rm(detrended_sales,detrended_stl_ts,stl_decomposition,trend_component)
```


```{r}
df_sales %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_sales <- df_sales %>%
  arrange(Date) %>%
  mutate(Sales_lag1 = lag(Sales, 1),
         Sales_lag3 = lag(Sales, 3),
         Sales_lag6 = lag(Sales, 6),
         Sales_lag9 = lag(Sales, 9),
         Sales_lag12 = lag(Sales, 12)) %>% 
  filter(!(Date < "2020-01-01"))

Splits <- initial_time_split(lag_df_sales, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, Sales,.interactive = TRUE)
```


Model Pre-Processing
```{r}
recipe_spec <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(Sales ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_sales
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_sales$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11, KPI_1,
         Promo_12, Cust_type_1, Cust_type_2) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(KPI_1 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_sales %>% select(Date,Sales), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(Sales_lag1 = lag(Sales, 1),
         Sales_lag3 = lag(Sales, 3),
         Sales_lag6 = lag(Sales, 6),
         Sales_lag9 = lag(Sales, 9),
         Sales_lag12 = lag(Sales, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(Sales)))

new_data <- df_combined %>%
  filter(is.na(Sales)) %>%
  select(-Sales) %>%
  filter(!(is.na(Sales_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = Sales,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,Sales,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           Promo_12,Sales_lag1,Sales_lag3,Sales_lag6,Sales_lag9,Sales_lag12,Cust_type_1,Cust_type_2)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(Sales)) %>% # Remove NAs in Sales
                        filter(!is.na(Sales_lag1)) %>% # Remove NAs in Sales_lag1
                        filter(!is.na(Sales_lag3)) %>%
                        filter(!is.na(Sales_lag6)) %>%
                        filter(!is.na(Sales_lag9)) %>%
                        filter(!is.na(Sales_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           Sales = forecasted_value,
                           Sales_lag1 = NA,
                           Sales_lag3 = NA,
                           Sales_lag6 = NA,
                           Sales_lag9 = NA,
                           Sales_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        Sales = if_else(Date == next_date, forecasted_value, Sales),
        Sales_lag1 = lag(Sales, 1),
        Sales_lag3 = lag(Sales, 3),
        Sales_lag6 = lag(Sales, 6),
        Sales_lag9 = lag(Sales, 9),
        Sales_lag12 = lag(Sales, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(Sales)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(Sales)) %>%
      select(-Sales) %>%
      filter(!(is.na(Sales_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/NativeSales_forecast.csv")
```


######################################################################################
#
# KPI_2
#
######################################################################################


###
# Cust_type_1
###


```{r}
# Load in Raw Data
df_KPI_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_KPI_2) #%>%
  #filter(Date > as.Date("2020-01-01"))

names(df_KPI_2) <- c("Date", "KPI_2")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),         
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)

###################################################################
# Reads in KPI_1
###

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/Cust_type_1_KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)
###################################################################
# Reads in Sales, OG code. Removing for this test iteration
###

#df_Sales <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  #mutate(Date = ymd(Date)) %>%
  #select(Date, Cust_type_1_Sales)

#names(df_Sales) <- c("Date", "Sales")

#df_Sales_Forecast <- read_csv("forecasts/Cust_type_1_NativeSales_forecast.csv")

# df_Sales_Forecast$.index <- mdy(df_Sales_Forecast$.index)

#df_Sales_Forecast <- df_Sales_Forecast[,c(1,4)]
#names(df_Sales_Forecast) <- c("Date", "Sales")

#df_Sales <- rbind(df_Sales, df_Sales_Forecast)

#rm(df_Sales_Forecast)
###################################################################

df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
#df_promos <- left_join(df_promos, df_Sales, by = "Date")
df_KPI_2 <- left_join(df_KPI_2, df_promos, by = "Date")

head(df_KPI_2)
```

```{r}
df_KPI_2 %>%
  ggplot(aes(Date, KPI_2)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_2 - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

```{r}
# STL Decomposition
detrended_Promo_6 <- df_KPI_2
stl_decomposition <- stl(ts(detrended_Promo_6$KPI_2, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_Promo_6$detrended_stl <- detrended_Promo_6$KPI_2 - trend_component

# Visualize
ggplot(detrended_Promo_6, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_2 - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_Promo_6$detrended_stl, lag.max = nrow(detrended_Promo_6), xlab="Lag (years)")
pacf(detrended_Promo_6$detrended_stl, lag.max = nrow(detrended_Promo_6), xlab="Lag (years)")

rm(detrended_Promo_6,trend_component,stl_decomposition)
```


```{r}
df_KPI_2 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_2 <- df_KPI_2 %>%
  arrange(Date) %>%
  mutate(KPI_2_lag1 = lag(KPI_2, 1),
         KPI_2_lag3 = lag(KPI_2, 3),
         KPI_2_lag6 = lag(KPI_2, 6),
         KPI_2_lag9 = lag(KPI_2, 9),
         KPI_2_lag12 = lag(KPI_2, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_KPI_2, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_2,.interactive = TRUE)
```


Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_ets_2,
    fit_ets_3,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_2
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_KPI_2$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11,KPI_1) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_2 %>% select(Date,KPI_2), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(KPI_2_lag1 = lag(KPI_2, 1),
         KPI_2_lag3 = lag(KPI_2, 3),
         KPI_2_lag6 = lag(KPI_2, 6),
         KPI_2_lag9 = lag(KPI_2, 9),
         KPI_2_lag12 = lag(KPI_2, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(KPI_2)))

new_data <- df_combined %>%
  filter(is.na(KPI_2)) %>%
  select(-KPI_2) %>%
  filter(!(is.na(KPI_2_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = KPI_2,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_2,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           KPI_2_lag1,KPI_2_lag3,KPI_2_lag6,KPI_2_lag9,KPI_2_lag12,KPI_1)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_2)) %>% # Remove NAs in KPI_2
                        filter(!is.na(KPI_2_lag1)) %>% # Remove NAs in KPI_2_lag1
                        filter(!is.na(KPI_2_lag3)) %>%
                        filter(!is.na(KPI_2_lag6)) %>%
                        filter(!is.na(KPI_2_lag9)) %>%
                        filter(!is.na(KPI_2_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_2 = forecasted_value,
                           KPI_2_lag1 = NA,
                           KPI_2_lag3 = NA,
                           KPI_2_lag6 = NA,
                           KPI_2_lag9 = NA,
                           KPI_2_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_2 = if_else(Date == next_date, forecasted_value, KPI_2),
        KPI_2_lag1 = lag(KPI_2, 1),
        KPI_2_lag3 = lag(KPI_2, 3),
        KPI_2_lag6 = lag(KPI_2, 6),
        KPI_2_lag9 = lag(KPI_2, 9),
        KPI_2_lag12 = lag(KPI_2, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_2)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_2)) %>%
      select(-KPI_2) %>%
      filter(!(is.na(KPI_2_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/Cust_type_1_KPI_2_forecast.csv")
```


###
# Cust_type_2
###


```{r}
# Load in Raw Data
df_KPI_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_KPI_2) #%>%
  #filter(Date > as.Date("2020-01-01"))

names(df_KPI_2) <- c("Date", "KPI_2")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)

###################################################################
# Reads in KPI_1, OG code. Removing for this test iteration
###

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/Cust_type_2_KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)
###################################################################
# Reads in Sales, OG code. Removing for this test iteration
###

#df_Sales <- read_xlsx("data/Forecast_Data.xlsx", sheet = "Native_Sales") %>%
  #mutate(Date = ymd(Date)) %>%
  #select(Date, Cust_type_2_Sales)

#names(df_Sales) <- c("Date", "Sales")

#df_Sales_Forecast <- read_csv("forecasts/Cust_type_2_NativeSales_forecast.csv")

# df_Sales_Forecast$.index <- mdy(df_Sales_Forecast$.index)

#df_Sales_Forecast <- df_Sales_Forecast[,c(1,4)]
#names(df_Sales_Forecast) <- c("Date", "Sales")

#df_Sales <- rbind(df_Sales, df_Sales_Forecast)

#rm(df_Sales_Forecast)
###################################################################

df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
#df_promos <- left_join(df_promos, df_Sales, by = "Date")
df_KPI_2 <- left_join(df_KPI_2, df_promos, by = "Date")

head(df_KPI_2)
```

```{r}
df_KPI_2 %>%
  ggplot(aes(Date, KPI_2)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_2 - Japan",
       x = "",
       y = "")
```

```{r}
# STL Decomposition
detrended_Promo_6 <- df_KPI_2
stl_decomposition <- stl(ts(detrended_Promo_6$KPI_2, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_Promo_6$detrended_stl <- detrended_Promo_6$KPI_2 - trend_component

# Visualize
ggplot(detrended_Promo_6, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_Promo_6$detrended_stl, lag.max = nrow(detrended_Promo_6), xlab="Lag (years)")
pacf(detrended_Promo_6$detrended_stl, lag.max = nrow(detrended_Promo_6), xlab="Lag (years)")

rm(detrended_Promo_6,trend_component,stl_decomposition)
```

```{r}
df_KPI_2 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_2 <- df_KPI_2 %>%
  arrange(Date) %>%
  mutate(KPI_2_lag1 = lag(KPI_2, 1),
         KPI_2_lag3 = lag(KPI_2, 3),
         KPI_2_lag6 = lag(KPI_2, 6),
         KPI_2_lag9 = lag(KPI_2, 9),
         KPI_2_lag12 = lag(KPI_2, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_KPI_2, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_2,.interactive = TRUE)
```

Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_2
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_KPI_2$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11, KPI_1) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_2 %>% select(Date,KPI_2), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(KPI_2_lag1 = lag(KPI_2, 1),
         KPI_2_lag3 = lag(KPI_2, 3),
         KPI_2_lag6 = lag(KPI_2, 6),
         KPI_2_lag9 = lag(KPI_2, 9),
         KPI_2_lag12 = lag(KPI_2, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(KPI_2)))

new_data <- df_combined %>%
  filter(is.na(KPI_2)) %>%
  select(-KPI_2) %>%
  filter(!(is.na(KPI_2_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = KPI_2,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_2,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           KPI_2_lag1,KPI_2_lag3,KPI_2_lag6,KPI_2_lag9,KPI_2_lag12,KPI_1)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_2)) %>% # Remove NAs in KPI_2
                        filter(!is.na(KPI_2_lag1)) # Remove NAs in KPI_2_lag1
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_2 = forecasted_value,
                           KPI_2_lag1 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_2 = if_else(Date == next_date, forecasted_value, KPI_2),
        KPI_2_lag1 = lag(KPI_2, 1)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_2)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_2)) %>%
      select(-KPI_2) %>%
      filter(!(is.na(KPI_2_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/Cust_type_2_KPI_2_forecast.csv")
```


###
# Acutal
###


```{r}
# Load in Raw Data
df_KPI_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, KPI_2)

names(df_KPI_2) <- c("Date", "KPI_2")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)

###################################################################
# Loads Cust_type_1 KPI_2 Forecast
###

df_Cust_type_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_KPI_2) 

names(df_Cust_type_1) <- c("Date", "Cust_type_1")

df_Cust_type_1_Forecast <- read_csv("forecasts/Cust_type_1_KPI_2_forecast.csv")

# df_KPI_1_Forecast$.index <- mdy(df_KPI_1_Forecast$.index)

df_Cust_type_1_Forecast <- df_Cust_type_1_Forecast[,c(1,4)]

names(df_Cust_type_1_Forecast) <- c("Date", "Cust_type_1")

df_Cust_type_1 <- rbind(df_Cust_type_1, df_Cust_type_1_Forecast)

rm(df_Cust_type_1_Forecast)
###################################################################
# Cust_type_2 KPI_2 forecast
###

df_Cust_type_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_KPI_2)

names(df_Cust_type_2) <- c("Date", "Cust_type_2")

df_Cust_type_2_Forecast <- read_csv("forecasts/Cust_type_2_KPI_2_forecast.csv")

# df_KPI_1_Forecast$.index <- mdy(df_KPI_1_Forecast$.index)

df_Cust_type_2_Forecast <- df_Cust_type_2_Forecast[,c(1,4)]

names(df_Cust_type_2_Forecast) <- c("Date", "Cust_type_2")

df_Cust_type_2 <- rbind(df_Cust_type_2, df_Cust_type_2_Forecast)

rm(df_Cust_type_2_Forecast)


###################################################################
# Reads in KPI_1, OG code. Removing for this test iteration
###

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_2_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)
###################################################################

df_promos <- left_join(df_promos, df_Cust_type_2, by = "Date")
df_promos <- left_join(df_promos, df_Cust_type_1, by = "Date")
df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
df_KPI_2 <- left_join(df_KPI_2, df_promos, by = "Date")

head(df_KPI_2)
```

```{r}
df_KPI_2 %>%
  ggplot(aes(Date, KPI_2)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_2 - Japan",
       x = "",
       y = "")
```

```{r}
# STL Decomposition
detrended_Promo_6 <- df_KPI_2
stl_decomposition <- stl(ts(detrended_Promo_6$KPI_2, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_Promo_6$detrended_stl <- detrended_Promo_6$KPI_2 - trend_component

# Visualize
ggplot(detrended_Promo_6, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_1 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_Promo_6$detrended_stl, lag.max = nrow(detrended_Promo_6), xlab="Lag (years)")
pacf(detrended_Promo_6$detrended_stl, lag.max = nrow(detrended_Promo_6), xlab="Lag (years)")

rm(detrended_Promo_6,trend_component,stl_decomposition)
```


```{r}
df_KPI_2 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_2 <- df_KPI_2 %>%
  arrange(Date) %>%
  mutate(KPI_2_lag1 = lag(KPI_2, 1),
         KPI_2_lag3 = lag(KPI_2, 3),
         KPI_2_lag6 = lag(KPI_2, 6),
         KPI_2_lag9 = lag(KPI_2, 9),
         KPI_2_lag12 = lag(KPI_2, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_KPI_2, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_2,.interactive = TRUE)
```


Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_2 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_2
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(df_KPI_2$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, Promo_10, Promo_5,Promo_11, 
         Cust_type_1, Cust_type_2, KPI_1)#,Promo_12) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_2 %>% select(Date,KPI_2), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(KPI_2_lag1 = lag(KPI_2, 1),
         KPI_2_lag3 = lag(KPI_2, 3),
         KPI_2_lag6 = lag(KPI_2, 6),
         KPI_2_lag9 = lag(KPI_2, 9),
         KPI_2_lag12 = lag(KPI_2, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(KPI_2)))

new_data <- df_combined %>%
  filter(is.na(KPI_2)) %>%
  select(-KPI_2) %>%
  filter(!(is.na(KPI_2_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = KPI_2,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_2,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           KPI_2_lag1,KPI_2_lag3,KPI_2_lag6,KPI_2_lag9,KPI_2_lag12, Cust_type_1,
           Cust_type_2, KPI_1)#,Promo_12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_2)) %>% # Remove NAs in KPI_2
                        filter(!is.na(KPI_2_lag1)) %>% # Remove NAs in KPI_2_lag1
                        filter(!is.na(KPI_2_lag3)) %>%
                        filter(!is.na(KPI_2_lag6)) %>%
                        filter(!is.na(KPI_2_lag9)) %>%
                        filter(!is.na(KPI_2_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_2 = forecasted_value,
                           KPI_2_lag1 = NA,
                           KPI_2_lag3 = NA,
                           KPI_2_lag6 = NA,
                           KPI_2_lag9 = NA,
                           KPI_2_lag12 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_2 = if_else(Date == next_date, forecasted_value, KPI_2),
        KPI_2_lag1 = lag(KPI_2, 1),
        KPI_2_lag3 = lag(KPI_2, 3),
        KPI_2_lag6 = lag(KPI_2, 6),
        KPI_2_lag9 = lag(KPI_2, 9),
        KPI_2_lag12 = lag(KPI_2, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_2)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_2)) %>%
      select(-KPI_2) %>%
      filter(!(is.na(KPI_2_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/KPI_2_forecast.csv")
```


######################################################################################
#
# KPI_3
#
######################################################################################


```{r}
# Load in Raw Data
df_KPI_3 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_3") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, KPI_3)

names(df_KPI_3) <- c("Date", "KPI_3")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)


###################################################################
# Loads Cust_type_1 KPI_2 Forecast
###

df_Cust_type_1_KPI_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, Cust_type_1_KPI_2) 

names(df_Cust_type_1_KPI_2) <- c("Date", "Cust_type_1_KPI_2")

df_Cust_type_1_KPI_2_Forecast <- read_csv("forecasts/Cust_type_1_KPI_2_forecast.csv")

df_Cust_type_1_KPI_2_Forecast <- df_Cust_type_1_KPI_2_Forecast[,c(1,4)]
names(df_Cust_type_1_KPI_2_Forecast) <- c("Date", "Cust_type_1_KPI_2")

df_Cust_type_1_KPI_2 <- rbind(df_Cust_type_1_KPI_2, df_Cust_type_1_KPI_2_Forecast)

rm(df_Cust_type_1_KPI_2_Forecast)


###################################################################
# Loads full KPI_2 Forecast
###

df_KPI_2 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_2") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, KPI_2) 

names(df_KPI_2) <- c("Date", "KPI_2")

df_KPI_2_Forecast <- read_csv("forecasts/KPI_2_forecast.csv")

df_KPI_2_Forecast <- df_KPI_2_Forecast[,c(1,4)]
names(df_KPI_2_Forecast) <- c("Date", "KPI_2")

df_KPI_2 <- rbind(df_KPI_2, df_KPI_2_Forecast)

rm(df_KPI_2_Forecast)
###################################################################

df_promos <- left_join(df_promos, df_KPI_2, by = "Date")
df_promos <- left_join(df_promos, df_Cust_type_1_KPI_2, by = "Date")
df_KPI_3 <- left_join(df_KPI_3, df_promos, by = "Date")

rm(df_Cust_type_1_KPI_2,df_KPI_2)
head(df_KPI_3)
```

```{r}
df_KPI_3 %>%
  ggplot(aes(Date, KPI_3)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_3 - Japan",
       x = "",
       y = "") + 
  theme_classic()
```

```{r}
# STL Decomposition
detrended_Promo_5 <- df_KPI_3
stl_decomposition <- stl(ts(detrended_Promo_5$KPI_3, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_Promo_5$detrended_stl <- detrended_Promo_5$KPI_3 - trend_component

# Visualize
ggplot(detrended_Promo_5, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_3 - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_Promo_5$detrended_stl, lag.max = nrow(detrended_Promo_5), xlab="Lag (years)")
pacf(detrended_Promo_5$detrended_stl, lag.max = nrow(detrended_Promo_5), xlab="Lag (years)")

rm(detrended_Promo_5,trend_component,stl_decomposition)
```


```{r}
df_KPI_3 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```

Data Preparation
```{r}
lag_df_KPI_3 <- df_KPI_3 %>%
  arrange(Date) %>%
  mutate(Promo_5_lag1 = lag(KPI_3, 1),
         Promo_5_lag3 = lag(KPI_3, 3),
         Promo_5_lag6 = lag(KPI_3, 6),
         Promo_5_lag9 = lag(KPI_3, 9),
         Promo_5_lag12 = lag(KPI_3, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_KPI_3, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, KPI_3,.interactive = TRUE)
```

Model Pre-Processing
```{r}
recipe_spec <- recipe(KPI_3 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(KPI_3 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(KPI_3 ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```

```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_3
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```

```{r}
dates <- KPI_1(df_KPI_3$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, KPI_2, Cust_type_1_KPI_2, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, 
         Promo_13, Promo_10, Promo_5, Promo_11) #Promo_12) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_3 %>% select(Date,KPI_3), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(Promo_5_lag1 = lag(KPI_3, 1),
         Promo_5_lag3 = lag(KPI_3, 3),
         Promo_5_lag6 = lag(KPI_3, 6),
         Promo_5_lag9 = lag(KPI_3, 9),
         Promo_5_lag12 = lag(KPI_3, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_sales_data <- df_combined %>%
  filter(!(is.na(KPI_3)))

new_data <- df_combined %>%
  filter(is.na(KPI_3)) %>%
  select(-KPI_3) %>%
  filter(!(is.na(Promo_5_lag1)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_sales_data
  
  modeltime_actual_data_format <- actual_sales_data %>% 
      mutate(
        .index = Date,
        .value = KPI_3,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,KPI_3,KPI_2,Cust_type_1_KPI_2,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,
           Promo_11,Promo_5,Promo_5_lag1,Promo_5_lag3,Promo_5_lag6,Promo_5_lag9,Promo_5_lag12)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(KPI_3)) %>% # Remove NAs in KPI_3
                        filter(!is.na(Promo_5_lag1)) %>% # Remove NAs in Promo_5_lag1
                        filter(!is.na(Promo_5_lag3)) %>%
                        filter(!is.na(Promo_5_lag6)) %>%
                        filter(!is.na(Promo_5_lag9)) %>%
                        filter(!is.na(Promo_5_lag12))
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           KPI_2 = forecasted_value,
                           Promo_5_lag1 = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        KPI_3 = if_else(Date == next_date, forecasted_value, KPI_3),
        Promo_5_lag1 = lag(KPI_3, 1),
        Promo_5_lag3 = lag(KPI_3, 3),
        Promo_5_lag6 = lag(KPI_3, 6),
        Promo_5_lag9 = lag(KPI_3, 9),
        Promo_5_lag12 = lag(KPI_3, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(KPI_3)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(KPI_3)) %>%
      select(-KPI_3) %>%
      filter(!(is.na(Promo_5_lag1)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_sales_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/KPI_3_forecast.csv")
```



######################################################################################
#
# KPI_4
#
######################################################################################

```{r}
# Load in Raw Data
df_KPI_4 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, "KPI_4_Purchasers")

names(df_KPI_4) <- c("Date", "KPI_4")

df_promos <- read_xlsx("data/Forecast_Data.xlsx", sheet = "JPN_Promos") %>%
  mutate(Date = ymd(Date),
         Promo_1 = as.integer(Promo_1),
         Promo_2 = as.integer(Promo_2),
         Promo_3 = as.integer(Promo_3),
         Promo_4 = as.integer(Promo_4),
         Promo_5 = as.integer(Promo_12),
         Promo_6 = as.integer(Promo_6),
         Promo_7 = as.integer(Promo_7),
         Promo_8 = as.integer(Promo_8),
         Promo_9 = as.integer(Promo_9),
         Promo_13 = as.integer(Promo_13),
         Promo_10 = as.integer(Promo_10),          
         Promo_11 = as.integer(Promo_11),
         Promo_12 = as.integer(Promo_12)) %>%
  select(-Promo_12) %>%
  select(-Promo_12)

#########################################

df_KPI_1 <- read_xlsx("data/Forecast_Data.xlsx", sheet = "KPI_1_Purchasers") %>%
  mutate(Date = ymd(Date)) %>%
  select(Date, KPI_1_Purchasers)

names(df_KPI_1) <- c("Date", "KPI_1")

df_KPI_1_Forecast <- read_csv("forecasts/KPI_1Purchasers_forecast.csv")

df_KPI_1_Forecast <- df_KPI_1_Forecast[,c(1,4)]

names(df_KPI_1_Forecast) <- c("Date", "KPI_1")

df_KPI_1 <- rbind(df_KPI_1, df_KPI_1_Forecast)

rm(df_KPI_1_Forecast)

###################################################################

df_promos <- left_join(df_promos, df_KPI_1, by = "Date")
df_KPI_4 <- left_join(df_KPI_4, df_promos, by = "Date")


head(df_KPI_4)
```


```{r}
df_KPI_4 %>%
  ggplot(aes(Date, `KPI_4`)) +
  geom_line() + 
  geom_point()+
  geom_smooth() +
  labs(title = "KPI_4 Purchasers - Japan",
       x = "",
       y = "") + 
  theme_classic()
```


```{r}
# STL Decomposition
detrended_KPI_4 <- df_KPI_4
stl_decomposition <- stl(ts(detrended_KPI_4$`KPI_4`, frequency = 12), s.window = "periodic")
trend_component <- stl_decomposition$time.series[, "trend"]
detrended_KPI_4$detrended_stl <- detrended_KPI_4$`KPI_4` - trend_component

# Visualize
ggplot(detrended_KPI_4, aes(Date, detrended_stl)) +
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "STL Detrended KPI_4 - Japan",
       x = "",
       y = "") + 
  theme_classic()

# Plot ACF (Autocorrelation) and PACF (Partial Autocorrelation) with more lags
acf(detrended_KPI_4$detrended_stl, lag.max = nrow(detrended_KPI_4), xlab="Lag (years)")
pacf(detrended_KPI_4$detrended_stl, lag.max = nrow(detrended_KPI_4), xlab="Lag (years)")

rm(detrended_KPI_4,stl_decomposition,trend_component)
```


```{r}
df_KPI_4 %>%
  select(-Date) %>%
  cor() %>%
  round(2)
```


```{r}
lag_df_KPI_4 <- df_KPI_4 %>%
  arrange(Date) %>%
  mutate(`KPI_4_lag1` = lag(`KPI_4`, 1),
         `KPI_4_lag3` = lag(`KPI_4`, 3),
         `KPI_4_lag6` = lag(`KPI_4`, 6),
         `KPI_4_lag9` = lag(`KPI_4`, 9),
         `KPI_4_lag12` = lag(`KPI_4`, 12)) %>% 
  drop_na()

Splits <- initial_time_split(lag_df_KPI_4, prop = 0.85)

Splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(Date, `KPI_4`,.interactive = TRUE)
```


```{r}
recipe_spec <- recipe(`KPI_4` ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_2 <- recipe(`KPI_4` ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 2) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) 

recipe_spec_3 <- recipe(`KPI_4` ~ ., training(Splits)) %>%
  step_timeseries_signature(Date) %>%
  step_fourier(Date, period = 12, K = 3) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  # step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

###########################
# Recipe 1
###########################

### ML Models
# Elastic Net
fit_glmnet <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet <- workflow() %>%
  add_model(fit_glmnet) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

###########################
### Non ML Moels
# Exponential Smoothing
fit_ets <- workflow() %>%
  add_model(exp_smoothing() %>% set_engine("ets")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))

# Prophet
fit_prophet <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec) %>%
  fit(training(Splits))


###########################
# Recipe 2
###########################

### ML Models
# Elastic Net
fit_glmnet_2 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_2 <- workflow() %>%
  add_model(fit_glmnet_2) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_2<- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_2 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_2 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_2 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_2 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))

###########################
### Non ML Moels

# Prophet
fit_prophet_2 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_2) %>%
  fit(training(Splits))


###########################
# Recipe 3
###########################

### ML Models
# Elastic Net
fit_glmnet_3 <- linear_reg(penalty = 0.1, mixture = 0.5) %>%
  set_engine("glmnet")
fit_glmnet_3 <- workflow() %>%
  add_model(fit_glmnet_3) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Random Forest
fit_rf_3 <- workflow() %>%
  add_model(rand_forest("regression") %>% set_engine("ranger")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Gradient Boost
fit_xgb_3 <- workflow() %>%
  add_model(boost_tree("regression") %>% set_engine("xgboost")) %>%
  add_recipe(recipe_spec_3 %>% step_rm(Date)) %>%
  fit(training(Splits))

# Prophet Boost Hybrid Model
fit_prophet_boost_3 <- workflow() %>%
  add_model(prophet_boost("regression", seasonality_yearly = TRUE) %>% set_engine("prophet_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

# Arima Boost
fit_arima_boosted_3 <- workflow() %>%
  add_model(arima_boost("regression") %>% set_engine("auto_arima_xgboost")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################
### Non ML Moels

# Prophet
fit_prophet_3 <- workflow() %>%
  add_model(prophet_reg() %>% set_engine("prophet")) %>%
  add_recipe(recipe_spec_3) %>%
  fit(training(Splits))

###########################

### Add fitted model to a Model Table
models_tbl <-
  modeltime_table(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3
  )
###########################

rm(
    fit_glmnet,
    fit_glmnet_2,
    fit_glmnet_3,
    fit_rf,
    fit_rf_2,
    fit_rf_3,
    fit_xgb,
    fit_xgb_2,
    fit_xgb_3,
    fit_prophet_boost,
    fit_prophet_boost_2,
    fit_prophet_boost_3,
    fit_arima_boosted,
    fit_arima_boosted_2,
    fit_arima_boosted_3,
    fit_ets,
    fit_prophet,
    fit_prophet_2,
    fit_prophet_3,
    recipe_spec,
    recipe_spec_2,
    recipe_spec_3
)

### Calibration
calibration_table <- models_tbl %>%
  modeltime_calibrate(new_data = testing(Splits))
```


```{r}
calibration_table %>%
  modeltime_forecast(
    new_data = testing(Splits),
    actual_data = lag_df_KPI_4
    ) %>%
  plot_modeltime_forecast(.interactive = TRUE)
```


```{r}
calibration_table %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(
    .interactive = FALSE
  )
```


```{r}
dates <- KPI_1(lag_df_KPI_4$Date)
`%ni%` <- Negate(`%in%`)

df_promos <- df_promos %>% 
  select(Date, KPI_1, Promo_1, Promo_2, Promo_3, Promo_4, Promo_6, Promo_7, Promo_8, Promo_9, Promo_13, 
         Promo_10, Promo_5, Promo_11) #%>%
  #filter(Date %ni% dates)

df_promos <- recipe(Promo_5 ~ ., df_promos) %>%
  step_timeseries_signature(Date) %>%
  step_rm(matches("(hour)|(minute)|(second)|(am.pm)|(xts)|(iso)|(lbl)")) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  prep() %>%
  juice()

head(df_promos)
```


```{r}
# Finds the min RMSE model that is not overfitting
min_rmse_model <- calibration_table %>%
  modeltime_accuracy() %>%
  filter(rsq < 0.97) %>%
  filter(rmse == min(rmse)) %>%
  select(.model_id) %>%
  pull()

#####
# Luke test forecast
#####

df_combined <- left_join(df_promos, 
                         df_KPI_4 %>% select(Date,`KPI_4`), 
                         by = "Date") %>% 
  arrange(Date)

df_combined <- df_combined  %>%
  mutate(`KPI_4_lag1` = lag(`KPI_4`, 1),
         `KPI_4_lag3` = lag(`KPI_4`, 3),
         `KPI_4_lag6` = lag(`KPI_4`, 6),
         `KPI_4_lag9` = lag(`KPI_4`, 9),
         `KPI_4_lag12` = lag(`KPI_4`, 12)) %>%
  filter(!(Date < "2020-01-01"))

actual_KPI_1_data <- df_combined %>%
  filter(!(is.na(`KPI_4`)))

new_data <- df_combined %>%
  filter(is.na(`KPI_4`)) %>%
  select(-`KPI_4`) %>%
  filter(!(is.na(`KPI_4_lag1`)))

# Defines how many months out you Cust_type_1nt to filter (6 = 6 months)
forecast_horizon <- 10

generate_forecast <- function(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon) {
  
  forecast_results <- actual_KPI_1_data
  
  modeltime_actual_data_format <- actual_KPI_1_data %>% 
      mutate(
        .index = Date,
        .value = `KPI_4`,
        .conf_lo = NA,
        .conf_hi = NA,
        .key = "actual",
        .model_desc = "ACTUAL",
        .model_id = NA
    ) %>%
    select(.index, .value, .conf_lo, .conf_hi, .key, .model_desc, .model_id)
  
  df_combined <- df_combined %>%
    select(Date,`KPI_4`,KPI_1,Promo_1,Promo_2,Promo_3,Promo_4,Promo_6,Promo_7,Promo_8,Promo_9,Promo_13,Promo_10,Promo_11,Promo_5,
           `KPI_4_lag1`,`KPI_4_lag3`,`KPI_4_lag6`,`KPI_4_lag9`,`KPI_4_lag12`)
  
  for (i in 1:forecast_horizon) {
    forecast <- calibration_table %>%
      filter(.model_id %in% min_rmse_model) %>%
      modeltime_refit(df_combined %>%
                        filter(!is.na(`KPI_4`)) %>% # Remove NAs in KPI_4
                        filter(!is.na(`KPI_4_lag1`)) %>% # Remove NAs in KPI_4_lag1
                        filter(!is.na(`KPI_4_lag3`)) %>%
                        filter(!is.na(`KPI_4_lag6`)) %>%
                        filter(!is.na(`KPI_4_lag9`)) %>%
                        filter(!is.na(`KPI_4_lag12`)) 
                      ) %>%
      modeltime_forecast(
        new_data = new_data,
        actual_data = forecast_results
      )
    
    # Extract the forecasted value
    forecasted_value <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .value) %>%
      slice_tail(n = 1) %>%
      pull(.value)
    
    # Extract the .conf_lo value
    forecasted_lo <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_lo) %>%
      slice_tail(n = 1) %>%
      pull(.conf_lo)
    
    # Extract the .conf_hi value
    forecasted_hi <- forecast %>%
      filter(.key == "prediction") %>%
      select(.index, .conf_hi) %>%
      slice_tail(n = 1) %>%
      pull(.conf_hi)
    
    # Add the forecasted value to the results
    next_date <- max(forecast_results$Date) + months(1)
    next_row <- data.frame(Date = next_date,
                           `KPI_4` = forecasted_value,
                           `KPI_4_lag1` = NA,
                           `KPI_4_lag3` = NA,
                           `KPI_4_lag6` = NA,
                           `KPI_4_lag9` = NA,
                           `KPI_4_lag12` = NA)
    
    forecast_results <- bind_rows(forecast_results, next_row)
    
    #Creates a separate forecast table in the Modeltime format
    Luke_forecast <- data.frame(
      .index = next_date,
      .value = forecasted_value,
      .conf_lo = forecasted_lo,
      .conf_hi = forecasted_hi,
      .key = "prediction",
      .model_desc = calibration_table %>%
        filter(.model_id %in% min_rmse_model) %>%
        pull(.model_desc),
      .model_id = min_rmse_model
    )
    
    modeltime_actual_data_format <- bind_rows(modeltime_actual_data_format,Luke_forecast)
    
    # Update lag_df_KPI_1 for next iteration
    df_combined <- df_combined %>%
      mutate(
        `KPI_4` = if_else(Date == next_date, forecasted_value, `KPI_4`),
        `KPI_4_lag1` = lag(`KPI_4`, 1),
        `KPI_4_lag3` = lag(`KPI_4`, 3),
        `KPI_4_lag6` = lag(`KPI_4`, 6),
        `KPI_4_lag9` = lag(`KPI_4`, 9),
        `KPI_4_lag12` = lag(`KPI_4`, 12)
      )
    
    # Updates forecast_results
    forecast_results <- df_combined %>% 
      filter(!(is.na(`KPI_4`)))
    
    # Update new_data for the next iteration
    new_data <- df_combined %>%
      filter(is.na(`KPI_4`)) %>%
      select(-`KPI_4`) %>%
      filter(!(is.na(`KPI_4_lag1`)))
  }
  
  return(modeltime_actual_data_format)
}

# Generates forecast
forecast_results <- generate_forecast(min_rmse_model, actual_KPI_1_data, df_combined, new_data, forecast_horizon)

forecast_results %>%
  plot_modeltime_forecast(.interactive = FALSE)

Export <- forecast_results %>%
  filter(.model_desc != "ACTUAL") %>%
  select(-.model_id, -.key) %>%
  spread(key = .model_desc, value = .value) %>%
  mutate(.index = ymd(.index))

write_csv(Export, "forecasts/KPI_4_forecast.csv")
```

